Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-07-01 Latex/rebuttal.txt

> Manuscript Number: OPHOTO-D-21-00020  
> Towards Spherical Robots For Mobile Mapping In Human Made
> Environments
> Dear Mr. Bredenbeck,     
> Thank you for submitting your manuscript to ISPRS Open Journal of
> Photogrammetry and Remote Sensing.

@@

> Further open questions/comments are:
> Page 1, Line 15: Double use of "protect", which should be replaced
> by another word.

We removed first instance.

> Page 1, Line 21: The link for the "second option" to the use of an
> IMU is not necessarily obvious.

We added IMU as sensor for coarse estimation.

> Page 1, Column 2, Line 52-56: Complicated sentence which should be
> reformulated.

We have split into two sentences

> Page 2, Column 2, Line 15: The term "long stop" is not to be
> interpreted clearly in this context. How is "long" defined in this
> sense in terms of time or space?

The specified stop is required to find enough points for plane
detection.

> Page 3, Column 1, Line 6-8: A specific reference should be given for
> the first half of the sentence, as reference 19 probably only refers
> to the second part.

FIXME! Added todo for Dorit/Andreas as they wrote this

> Page 3, Column 1, Line 23-26: Not all variables were introduced
> accurately

We have introduced missing variables and clarified rho.

@@

> Page 3, Column 1, Line 33-34: Selection of references for this?

We have added plane segmentation sources.

> Page 3, Column 1, Line 34-35: But what demands are made on the
> assignment? This is unclear to the reader, also in connection with
> the general quality requirements of the whole approach.

We have added a specification for "good enough for plane detection".

> Page 3, Column 1, Line 38: How can the threshold value be specified,
> since it is probably not identical for all applications and
> environments? Later, there is also no indication of the choice of
> the value in the own simulated and real data sets.

FIXME: Added todo for Fabi

> Page 3, Column 1, Line 50: What does the index k describe and what
> is the difference to the index i from Section 3.2?

We have clarified indeces k=planes i=points.

> Page 3, Equation (1): Again, some variables are not specified. For
> example, the source of tx ty tz is unclear.

We have introduced tx ty tz properly.

> Page 3, Equation (3): Equation unclear regarding the use of the 2 in
> the exponent as well as the index.

We have specified that we're using the square of the L2 norm.

> Page 3, Equations (4)-(5): Here I don't understand how to get to the
> elements of the normal vector through the transformation. Moreover,
> these individual elements were not introduced in advance.

We have corrected indeces and introduced the elements.

> Page 3, Equation (9): The variable alpha is not described and
> explained

An explaination of alpha was added.

> Page 4, Equation (10): Description of the individual variables is
> missing and, moreover, rho has already been used as the distance
> parameter of the Hesse-normal form

we have replaced rho with zeta and introduced the variables.

> Page 4, Equation (12): Is epsilon here the same variable as the
> threshold in Section 3.3? Probably not.

We have renamed epsilon and clarified the difference to sec 3.3.

> Page 4, Column 2, Line 15: "some dimensions": Which ones and why
> exactly are they chosen? Are they the same ones all the time?

FIXME: chose better example, added todo for Fabi

@@

> Page 4, Column 2, Line 20-25: Reference is missing

We haded a citation.

> Page 4, Column 2, Line 55: Doubled information regarding the
> distance measurement precision

We removed duplicated information.

> Page 5, Column 1, Equation (18): Delta t is not introduced and there
> is no indication of how large the time steps are in the simulation.

We have introduced delta t and give a default value.

@@

> Page 5, Column 2, Line 14: Should it be "out" or "our"?

We have corrected this.

> Page 5, Column 2, Line 27-28: What are the specifications of the
> used IMU with regard to its uncertainty budget?

We have added precision of IMU and added the source.

> Page 6, Figure 1: How are these values to be interpreted and from
> where are they derived? This is unclear.

We have specified this. It is chosen to still allow plane detection.

> Page 8, Column 1, Table 1: What is missing is a classification of
> the values in relation to the expectations / demands...which are,
> however, still missing in advance

FIXME: -> I don't understand this comment? TODO

> Page 8, Column 1, Line 37-43: At this point, an interpretation of
> the significant second peak in the right-hand diagram in Figure 4
> should be made. This has not been discussed so far.

FIXME: -> added todo REDO experiment

> Page 8, Column 1, Line 51: "ten scans" means ten individual scan
> lines or 10 epochs or is this identical? What kind of temporal
> offset is there in between and wouldn't a motion model have to be
> taken into account for this or is an identical pose assumed for the
> ten scans?

We have specified which scans and that we assuem constant pose.

@@

> Page 8, Column 1, Line 55-56: What could be the cause of this?

We have specified the outlier dependence.

> Page 8, Column 2, Line 44: This sentence always applies and should
> not remain here.

We have removed this sentence.

> Page 9, Figure 4: The two point clouds in the middle of figure 4 are
> difficult to interpret in terms of their orientation. Could it be an
> option to add a coordinate system?

It was specified in the figure label that lateral images have the same
orientation.

### 2021-07-03 Latex/rebuttal.txt

 
> Manuscript Number: OPHOTO-D-21-00020  
> Towards Spherical Robots For Mobile Mapping In Human Made
> Environments
>
> Dear Mr. Bredenbeck,     
> 
> Thank you for submitting your manuscript to ISPRS Open Journal of
> Photogrammetry and Remote Sensing.
> 
> I have completed my evaluation of your manuscript. The reviewers
> recommend reconsideration of your manuscript following revision. I
> invite you to resubmit your manuscript after addressing the comments
> below. Please resubmit your revised manuscript by Jul 13, 2021.  
> When revising your manuscript, please consider all issues mentioned
> in the reviewers' comments carefully: please outline in a cover
> letter every change made in response to their comments and provide
> suitable rebuttals for any comments not addressed. Please note that
> your revised submission may need to be re-reviewed.     
> 
> To submit your revised manuscript, please log in as an author at
> https://www.editorialmanager.com/ophoto/, and navigate to the
> "Submissions Needing Revision" folder under the Author Main Menu.
> 
> ISPRS Open Journal of Photogrammetry and Remote Sensing values your
> contribution and I look forward to receiving your revised
> manuscript.
>   
> Kind regards,     
> 
> George Vosselman   
> Editor-in-Chief   
> ISPRS Open Journal of Photogrammetry and Remote Sensing    
>  
> Editor and Reviewer Comments:     
> 
> Editor:
> As you will see below both reviewers appreciate your work and don't
> have concerns regarding the methodology or results. Reviewers, in
> particular Reviewer 2, however, do have a large number of
> recommendations to improve the readability of your manuscript. Given
> the number of recommendations, I ask for a major revision. The
> recommendations should, however, be easy to implement.
>  
>   
> Reviewer 1: The manuscript presents the concept of a spherical
> mobile mapping system, and a data registration method utilizing the
> geometric constraints available in human-made environments,
> e.g. planar surfaces.
> 
> The manuscript has novel content and is well written, and can be
> accepted after minor revision. My comments and suggestions to be
> considered by the authors are as follows:
> 
> Lines 27-31: Spherical shell can protect the sensors inside, but
> this does not prevent the external disturbances such as dust or
> other impurity staining the sphere itself, affecting the performance
> of the system. So in principle this does not change the situation
> from using protective covers on "traditional" mobile mapping
> systems.

We clarified that the shell can enclose all sensor without requiring a 
number of points of connection as individual enlosings for all sensors
would. Further we added the requirement, that the shell is very 
durable.

> Lines 111-116: Modern kinematic scanning systems collect point cloud
> data with high speed, so also kinematic point clouds are often dense
> enough for robust plane determination. And on the other hand, sparse
> point clouds are not optimal for point-to-point matching due to the
> long distances between adjacent points.

We clarified that also the lilmited FOV plays a role in not finding 
planes for robust correspondences. 
FIXME @Andreas and @Dorit: I (Anton) disagree can you double check?

> Lines 244-246: The Livox ranging precision is given twice in this
> sentence.
> 
> Figure 4: The x-scale is given in figure caption, but I would
> suggest adding it to the figure also.

FIXME Redoing the experiment anyways

> Conclusion: Whereas the title, Abstract and Introduction concentrate
> mostly on the spherical mobile mapping, Conclusion deals almost
> entirely with the topic of registration, thus feeling somewhat
> separated from the rest of the manuscript. Reading the Conclusion,
> one could not expect that the title of the manuscript is "Towards
> Spherical Robots For Mobile Mapping In Human Made Environments".

We added more context about spherical robots and put the registration 
method into context.

### 2021-07-03 Latex/sections/conclusion.tex
Done reviewer 2 additional points corrections
Done reviewer one comments

In this paper, we have proposed a registration method for man made environments that exploits the structure of those environments. 
Given that in human-made environments parallel planes and right angles are abundantly available, we employ point-to-plane correspondences to improve a pre-registered 3D point cloud. 
We have evaluated the procedure on a simulated dataset and on an experimentally acquired dataset with different motion profiles. 
In this evaluation, we have shown that the procedure improves both datasets and yields maps that better resemble human-made, structures. 
In particular, the qualitative structure of the environments is reconstructed well. 
In the resulting maps, the parallel walls are clearly improved.

However, as section~\ref{sec:experimentalSetup} shows, some outliers remain in the registered point cloud due to the simplistic point-to-plane correspondence model.
This to be improved in future studies.
One idea to do so is to employ a local clustering technique onto the individual scans before registering them globally. 
Points from the scan with a similar normal get clustered together if their distance is small enough.
This way, a cluster represents a local plane while at the same time storing all the points that belong to that plane.
Point-to-plane correspondences then arise from the intersection of local clusters with global planes.

Needless to say, a lot of work remains to be done. 
%
Right now, not all steps in the procedure are autonomous, in particular the parameter tuning. 
In the future, one goal is to increase the autonomy of the system.
One approach is to introduce soft-locks for the optimization dimensions.
I.e., instead of locking some dimensions entirely from being used for optimization, they are weighted based on the dynamics of the system that encode which noise source is more likely.  
%
Currently, we are assembling the sphere of Figure~\ref{fig:robotRender} to test it in real environments.
Unfortunately, this sphere will be too large to fit our floating setup, thus it will be tested in an office like environment.
Furthermore, we will test our rolling and scanning spheres on a rail system to achieve repeatable trajectories.

>>>>

In this paper, we proposed an approach to mobile mapping using a spherical robot. 
Using the inherent rotation of the sphere used for locomotion to also rotate a laser scanner also for measurements of the entire environment.
We propose to post-process the acquire data using a novel registration method for man made environments that exploits the structure of those environments. 
Given that in human-made environments straight planes are abundantly available, we employ point-to-plane correspondences to improve a pre-registered 3D point cloud. 
We have evaluated the procedure on a simulated dataset and on an experimentally acquired dataset with different motion profiles. 
In this evaluation, we have shown that the procedure improves both datasets and yields maps that better resemble human-made, structures. 
In particular, the qualitative structure of the environments is reconstructed well. 
In the resulting maps, the parallel walls are clearly improved.

However, as section~\ref{sec:experimentalSetup} shows, some outliers remain in the registered point cloud due to the simplistic point-to-plane correspondence model.
This is to be improved in future studies.
One idea to do so is to employ a local clustering technique onto the individual scans before registering them globally. 
Points from the scan with a similar normal get clustered together if their distance is small enough.
This way, a cluster represents a local plane while at the same time storing all the points that belong to that plane.
Point-to-plane correspondences then arise from the intersection of local clusters with global planes.

%
Right now, not all steps in the procedure are autonomous, in particular the parameter tuning. 
In the future, one goal is to increase the autonomy of the system.
One approach is to introduce soft-locks for the optimization dimensions.
I.e., instead of locking some dimensions entirely from being used for optimization, they are weighted based on the dynamics of the system that encode which noise source is more likely.  
%
Currently, we are assembling the sphere of Figure~\ref{fig:robotRender} to test it in real environments.
Unfortunately, this sphere will be too large to fit our floating setup, thus it will be tested in an office like environment.
Furthermore, we will test our rolling and scanning spheres on a rail system to achieve repeatable trajectories.
